Maximum Likelihood Distillation for Robust Modulation Classification \thanks{This work has been sponsored by armasuisse Science and Technology under the project ARNO (project code ARAMIS 047-22).}

### 2022-10-25 paper/main.tex
Add Pascal final feedback

\begin{abstract}
Deep Neural Networks are being extensively used in communication systems and Automatic Modulation Classification (AMC) in particular. However, they are very susceptible to small adversarial perturbations that are carefully crafted to change the network decision. In this work, we build on knowledge distillation ideas and adversarial training in order to build more robust AMC systems. We first outline the importance of the quality of the training data in terms of accuracy and robustness of the model. We then propose to use the Maximum Likelihood function, which could solve the AMC problem in offline settings, to generate better training labels. Those labels teach the model to be uncertain in challenging conditions, which permits to increase the accuracy, as well as the robustness of the model when combined with adversarial training. Interestingly, we observe that this increase in performance transfers to online settings, where the Maximum Likelihood function cannot be used in practice. Overall, this work highlights the potential of learning to be uncertain in difficult scenarios, compared to directly removing label noise.
%\pf{add some quantitative notes or more precise information about the actual results.}\pf{recall contributions/benefits or add general perspectives about the potential of the proposal: so what? why is that a cool idea, a cool paper?} \pf{re-check the full paragraph}
\end{abstract}

@@

% AMC, deep learning is being used. Different solutions
Communication systems often require the receiver to recognize the modulation scheme that has been used to encode the transmitted signals. The task is often referred to as Automatic Modulation Classification (AMC) and has applications ranging from detecting daily radio stations and managing spectrum resources, to eavesdropping and interfering with radio communications. The AMC task can be formulated as a Maximum likelihood (ML) estimation problem \cite{huan1995likelihood,dobre2007survey,hameed2009likelihood}, by computing the maximum of the likelihood function of the received signal with all possible modulations. Even if the solution is Bayes-optimal, sub-optimal approximations are used in practice \cite{dobre2007survey,Hameed_Dobre_Popescu_2009} because ML requires prior knowledge of the channel characteristics and is computationally complex to solve in realtime.

Deep learning \cite{goodfellow2016deep} has been proposed as a better solution for AMC as neural networks are relatively fast at inference time, adaptable to any channel characteristics, and their performance scales well with large quantities of data. Two classes of architectures have been proposed for this task: long short-term memory networks (LSTMs) \cite{Rajendran_Meert_Giustiniano_Lenders_Pollin_2018,Guo_Jiang_Wu_Zhou_2020} and convolutional neural networks (CNNs) \cite{OShea_Corgan_Clancy_2016,West_OShea_2017,Sadeghi_Larsson_2019}. Particularly, the authors in \cite{OShea_Roy_Clancy_2018} use a model based on the ResNet architecture \cite{Szegedy_Ioffe_Vanhoucke_Alemi_2016}, that outperforms all other CNN architectures. Other works use neural architecture search (NAS) \cite{ahmadi2008modulation,dai2019multi,perenda2021evolutionary} to trade off performance with computational speed. Even though neural networks are currently the main and most effective method that tackles the AMC problem \cite{OShea_Roy_Clancy_2018}, they are very susceptible to adversarial perturbations, which compromises the security of the system against malicious attacks  \cite{Szegedy_Zaremba_Sutskever_Bruna_Erhan_Goodfellow_Fergus_2014, moosavi2017universal,Sadeghi_Larsson_2019,Lin_Zhao_2020,Flowers_Buehrer_Headley_2019, maroto2021benefits}. 
%\pf{that one can be shortened a bit if needed.}

@@

% Effect of adversarial perturbations.
% TODO: maybe add motivation of why robust models are important
%
Adversarial perturbations are carefully crafted but almost imperceptible disturbances that are added to the transmitted signal. These adversarial perturbations can be used as an effective way of jamming wireless communication systems as they require much less energy than normal attacks. Algorithms like FGSM \cite{Goodfellow_Shlens_Szegedy_2015} or PGD \cite{Madry_Makelov_Schmidt_Tsipras_Vladu_2019} can compute such perturbations by solving the following optimization problem:
\begin{equation}
\label{eq:adv_pert}
    \delta_i^* = \argmax_{\delta_i}\Ls(f_{\theta}(x_i + \delta_i), y_i) \quad \text{s.t.} \quad \lVert \delta_i \rVert_{\infty} \leq \varepsilon
\end{equation}
where $\delta_i^*$ is the adversarial perturbation added to the received signal $x_i$, $y_i$ is the one-hot-encoded vector of length K that encodes the modulation used, $\Ls$ is the cross-entropy loss, $f_{\theta}$ is the neural network defined with weights $\theta$, and $\varepsilon$ is a fixed value that constrains the norm of the perturbation to be small and imperceptible.

Among the defenses proposed to increase the adversarial robustness of AMC models, adversarial training \cite{maroto2021safeamc,manoj2022toward}, randomized smoothing \cite{kim2021channel,manoj2022toward} and Generative Adversarial Networks (GANs) \cite{wang2022gan} have been shown to be effective. But, in addition to being computationally costly, these defenses greatly reduce the accuracy of the model on clean data.
%\pf{be clear on limitations of the above}.

In contrast, some works from computer vision have tried to understand why networks are susceptible, and label noise has been pointed to as one of the main causes \cite{sanyal2020benign}. Knowledge distillation~\cite{hinton2015distilling,romero2014fitnets,zagoruyko2016paying,chebotar2016distilling} can reduce this effect by training a student model to match the outputs of a teacher model. While knowledge distillation has been used in AMC~\cite{ma2020cross}, some computer vision works~\cite{goldblum2020adversarially,zi2021revisiting,shao2021and,maroto2022benefits} have shown that to achieve adversarial robustness, the outputs of the student model have to be matched on adversarial examples as well. However, to achieve a significant increase in robustness, both the teacher and the student model have to be trained adversarially, which can be very costly computationally. 
%\pf{if the above works do not play with KD in AMC, say it clearly} \pf{outline clearly the limitations of other KD works...}

% % Defenses. Relationship with data. Knowledge distillation
% Some defenses have been proposed to make networks more robust, like adversarial training \cite{Madry_Makelov_Schmidt_Tsipras_Vladu_2019}, but it comes at a cost in accuracy and computational time.

% Our work, what are the main motivations. Contributions.
In this work, we build on the above observations and propose a new data-centric method to make neural networks more accurate and robust to adversarial attacks. We make the hypothesis that the information given by the original labels is limited, and does not encode the difference in uncertainty between low and high SNR signals. Therefore, we propose to bring better information to the model 
%\pf{is it formally noise? or uncertainties of some form?} 
by distilling the theoretical class probabilities derived from the offline maximum likelihood function estimation. We show that such knowledge distillation permits to achieve better accuracy and adversarial robustness, compared with using the original labels or removing label noise. We find similar increases in performance when we combine this approach with adversarial training, where we train the model to match the distilled labels on adversarial examples. We highlight that despite maximum likelihood being limited to offline settings, we see a clear benefit in the resulting model on online settings. We claim that helping the model be uncertain in challenging scenarios is a promising direction with relevance outside of AMC settings, further validating the intuition that the choice and the quality of the training data are highly influential on the adversarial robustness of the model.
%\pf{talk about the robustness aspects, and adversarial training, how is it performed} \pf{talk about robustness results} \pf{recall benefits of the proposal, provide perspectives... how great is that? where do we go from there?}

@@

The communication system that characterizes the AMC task is shown in Figure \ref{fig:comm_system} with the gray blocks. It is composed of the transmitter, the communication channel, and the receptor. The transmitter is composed of a modulator and a communication filter $r'(x)$. The modulator uses a specific mapping to convert the data into a sequence of symbols. The symbols are upsampled and passed through the communication filter (e.g. root-raised cosine) to avoid inter-symbol interference (ISI). The signal is transmitted through the communication channel, which inevitably adds noise and distortion to the signal. The receptor receives that signal, and it is composed of another communication filter $r(x)$, that downsamples and transforms the signal back into symbols, and the demodulator, which converts the symbols into data.

Automatically choosing the correct demodulator based on the signal received is the problem AMC tries to solve. 
In practice, we distinguish between two scenarios: the coherent scenario, where we have complete knowledge of the system and it is only assumed in offline settings, and the non-coherent scenario, where some or all the channel and transmitter characteristics are unknown. The latter is generally used in online settings and to test the model effectiveness in real conditions.

%Normally, to perform well on AMC, neural networks are trained to infer the modulation used in transmission from the signal received. Thus, the network will be optimized to be as confident and accurate as possible on the training set. However, while enforcing the network to accurately solve the task is feasible for signals with high SNR, on noisier signals typically there is a non-negligible probability that the signal received was generated from a different modulation than the one we are enforcing the model to predict. Such cases are numerous when testing models in the AMC literature, where the signal received could have been generated from any of multiple modulations with similar probability.
When training neural networks to perform well in AMC or any other task, they are optimized to be as confident and accurate as possible on a given training set. In the case of AMC, the set is composed of the received signals and their corresponding labels describing the modulation used in the form of one hot encoded vectors. Our claim is that these labels are not good enough to train the model in the AMC task. The reason is that for noisier and heavily distorted signals, there is a non-negligible probability that the signal received was generated from a different modulation than the one we are enforcing the model to predict. Such cases are numerous when testing models in the AMC literature. Thus, to properly distinguish between cleaner and noisier signals, we want to give the model more information that conveys the fact that there are signals where it should not be confident in its prediction. Luckily, in AMC there is an analytical model that is able to measure this uncertainty in coherent scenarios: the Maximum likelihood function.

@@

%In many other tasks, it can be difficult or even impossible to estimate the true probability of a sample belonging to a particular class. However, in AMC, we can use the Maximum likelihood (ML) function to derive these probabilities. Due to the characteristics of ML, this is only computationally feasible in coherent scenarios, where we have prior knowledge of the channel conditions. Particularly, if we assume the channel is gaussian with variance $\sigma^{2}$, and given the received symbols $r(x)$, where $r$ applies the proper communication filter and downsampling to the received signal. We show in Figure \ref{fig:comm_system} a diagram describing the communication system. We highlight that while the neural network has to process directly what the receptor receives, maximum likelihood processes the symbols of that signal instead. This is possible because we can assume we know the communication filter and upsampling used in the transmitter, which we can invert at the receptor. The ML function when the channel is gaussian is given by the following expression
In many other tasks, it can be difficult or even impossible to estimate the true probability of a sample belonging to a particular class. However, in AMC, we can use the Maximum likelihood (ML) function to derive these probabilities. Due to the characteristics of ML, this is only computationally feasible in coherent scenarios, where we have prior knowledge of the channel conditions. Particularly, if we assume the channel is gaussian with variance $\sigma^{2}$, and that we know the proper communication filter $r(\cdot)$ that matches the filter $r'(\cdot)$ used in transmission, then the ML function is given by the following expression
\begin{equation}
	f_{i}(r(x)) = \dfrac{1}{2\pi \sigma^{2}|M_i|}\prod_{t=1}^{T} \sum_{j=1}^{|M_i|} \exp\left(-\dfrac{\lVert r(x)_t - s_j\rVert^{2}}{2 \sigma^{2}}\right)
\label{eq:ml}
\end{equation}
where $f_{i}$ is the ML function for a given modulation $M_i$ with $|M_i|$ number of states, $T$ is the number of symbols, $x$ is the received signal before the communication filter, $r(x)_t$ is the t-th symbol received, and $s_j$ is the symbol that correspond to the state $j$. Given a set of modulations, the probability of a modulation $M_i$ would be $p_{ML}^{(i)}(x) = \log(f_{i}(r(x))) / \sum_i \log(f_{i}(r(x)))$. Note that the ML function directly processes $r(x)$ instead of $x$, as shown in Figure \ref{fig:comm_system}.

The reason why ML is not preferred over neural networks is simple: they perform badly in non-coherent scenarios, where the channel or transmission filter parameters are unknown. Moreover, any small deviation from the real channel parameters has a major effect on the ML performance, which discards the possibility of trying to estimate these parameters. Moreover, incorporating the parameter uncertainty in the ML formulation makes it much more costly computationally without being more performant than neural networks.

Based on these limitations, we propose a hybrid approach. We will use a neural network for inference, but we will train it with the probabilities given by ML, to give the model this additional uncertainty information. Because \eqref{eq:ml} is limited to gaussian channels, we will remove the Rayleigh/Rician component of the channel when computing the ML probabilities. This is feasible when we consider that we can have full knowledge of the channel conditions by generating the training samples ourselves. Moreover, after training the neural network, ML is no longer needed, enabling our model to be used in non-coherent scenarios, which model real communication systems.

@@

%Typically in AMC, neural networks try to fit a function that takes as input the received signal data and outputs the modulation used by the transmitter. Thus, the corresponding loss that the model uses to train is given by the standard training loss
In the AMC literature, neural networks are generally trained with the standard training (ST) loss
\begin{equation}
    \text{ST} : \dfrac{1}{N}\sum_{i}\Ls(f_{\theta}(x_i), y_i)
\end{equation}
where $N$ is the size of the training set.

%However, in practice, the neural network is trained with noisy signals where the modulation that was used cannot be inferred so easily. Intuitively, for these signals we would like the outputs of the network to rely on this sense of uncertainty. Thus, with similar principles as knowledge distillation, we propose to match the neural network outputs with the output of ML in the corresponding coherent scenario.
However, our proposal is to give the model labels that better express the uncertainty of highly corrupted signals. Thus, using similar principles as knowledge distillation, we propose to match the neural network outputs with the output of ML in its corresponding coherent scenario.
\begin{equation}
    \text{ST\_ML} : \dfrac{1}{N}\sum_{i}\Ls(f_{\theta}(x_i), p_{ML}(r(x_i)))
\label{eq:st_ml}
\end{equation}
where $p_{ML}$ gives the class probabilities from applying the Maximum Likelihood function, and $r$ is the function that uses the coupled receiver filter and downsamples the signal. Because $r$ and $p_{ML}$ are functions that depend on information that is not known in non-coherent scenarios, we propose to use this loss function only when training the network, where this information can be known.

The main downside of using this function is that, while the probabilities given by ML are optimal in the context of a coherent scenario, they differ from the real probabilities $p^{*}$ that are conditional to the channel and communication filter distributions, $H$. However, our hypothesis, which we test in Section \ref{sec:experiments}, is that training with $p_{ML}$ is going to be a better match to the optimal probabilities $p^{*}$ than the labels $y$ themselves, which enforce full confidence on all samples, no matter how noisy they are. Mathematically, these probabilities are related by the following expression:
\begin{equation}
	p[m|x] =  \sum_i p[m|x,H=h_i] \cdot p[H=h_i|x]
\end{equation}
where $m$ is the vector of all modulations, $h_i$ is one of the possible coherent scenarios where the true coherent scenario is assigned to $h_0$ without loss of generality. Thus, $p[m|x] = p^{*}$ and $p_{ML} = p[m|x,H=h_0]$. Based on this formulation, our model will match better $p^{*}$ when the true communication parameters $H=h_0$ can be easily predicted from x ($p[H=h_0|x] \approx 1$) or when the communication parameters do not affect that much the probabilities ($p[m|x,H=h_i] \approx p_{ML} \; \forall i$).

Additionally, we propose a middle-ground approach, where instead of training the model on the ML probabilities, we use these probabilities to determine if the true label is incorrect. This happens in very noisy scenarios, where the noise added to the signal may change the true class of the signal by pure chance. Intuitively, training on these signals will potentially confuse the network. Thus, we will use the standard training loss but training only on the signals without label noise:
\begin{equation}
    \text{ST\_LNR} : \dfrac{1}{|D|}\sum_{i \in D}\Ls(f_{\theta}(x_i), y_i)
\end{equation}
where a training signal $i$ is in the subset $D$ if and only if $\argmax(y_i) = \argmax(p_{ML}(r(x_i)))$.

@@

There are multiple reasons why we want neural networks to be robust against adversarial perturbations. Not only it enables secure systems against adversarial attacks, but robust models are also more interpretable, basing their decisions on sensible features for the AMC task, like the quadrature and in phase components of the symbols \cite{maroto2021safeamc}. One of the most straightforward ways to improve the network robustness is to use the adversarial training (AT) loss function
\begin{equation}
    \text{AT} : \dfrac{1}{N}\sum_{i}\Ls(f_{\theta}(x_i'), y_i)
\end{equation}
where $x_i' = x_i + \delta_i^*$ is a crafted adversarial signal that maximizes the cross-entropy loss of the neural network in the neighborhood of $x_i$. Because the adversarial perturbation is dependent on the model weights, it has to be computed at each training iteration, typically using PGD.

Analogously to \eqref{eq:st_ml}, we propose the following loss, in which the original labels are replaced with the ML probabilities:
\begin{equation}
    \text{AT\_ML} : \dfrac{1}{N}\sum_{i}\Ls(f_{\theta}(x_i'), p_{ML}(r(x_i')))
\end{equation}
We highlight that the ML function assumes the signal was distorted with gaussian noise, which is no longer since the input was adversarially perturbed. However, during adversarial training the adversarial perturbation used is very small, so we can make the assumption that the combination of the channel gaussian noise and the adversarial noise is approximately gaussian with energy $\sigma_F^{2} = \sigma^{2} + \varepsilon^{2}$.

One way to reduce the effect of this assumption is to instead remove label noise using ML
\begin{equation}
    \text{AT\_LNR} : \dfrac{1}{|D|}\sum_{i \in D}\Ls(f_{\theta}(x_i'), y_i)
\end{equation}
where a training signal $i$ is in the subset $D$ if and only if $\argmax(y_i) = \argmax(p_{ML}(r(x_i')))$. Even if $p_{ML}$ is not strictly correct due to the adversarial perturbation being relatively large, it will tend to remove signals that are already very noisy, thus greatly reducing the chance of label noise affecting adversarial training. Since label noise has a direct impact on the robustness of the network, we expect label noise removal to be particularly effective.

For training with non-gaussian channels, because we remove the Rayleigh/Rician components for the ML function, we have the drawback that we cannot directly translate the adversarial perturbation added to the neural network to the signal received by ML. For that reason, we have considered the following two solutions: to use the ML probabilities of the uncorrupted signal
\begin{equation}
    \text{AT\_NML} : \dfrac{1}{N}\sum_{i}\Ls(f_{\theta}(x_i'), p_{ML}(r(g_i))
\label{eq:at_nml}
\end{equation}
and to use the adversarial example given by the ML function
\begin{equation}
    \text{AT\_AML} : \dfrac{1}{N}\sum_{i}\Ls(f_{\theta}(x_i'), p_{ML}(r(g_i)'))
	\label{eq:at_aml}
\end{equation}
where $g_i$ is the received signal after removing the Rayleigh/Rician components, and $r(g_i)'$ is a crafted adversarial signal that maximizes the cross-entropy loss of ML in the neighborhood of $r(g_i)$.
Because adversarial attacks can significantly change the probabilities of the received signal, we recommend to use AT\_AML over AT\_NML.

@@

We propose to evaluate our methodology on scenarios with different levels of non-coherence. This way, we can verify if the probabilities generated by ML in a coherent scenario are useful to train the model even if it is tested on varying channel and transmitter conditions.

>>>>

\begin{abstract}
Deep Neural Networks are being extensively used in communication systems and Automatic Modulation Classification (AMC) in particular. However, they are very susceptible to small adversarial perturbations that are carefully crafted to change the network decision. In this work, we build on knowledge distillation ideas and adversarial training in order to build more robust AMC systems. We first outline the importance of the quality of the training data in terms of accuracy and robustness of the model. We then propose to use the Maximum Likelihood function, which could solve the AMC problem in offline settings, to generate better training labels. Those labels teach the model to be uncertain in challenging conditions, which permits to increase the accuracy, as well as the robustness of the model when combined with adversarial training. Interestingly, we observe that this increase in performance transfers to online settings, where the Maximum Likelihood function cannot be used in practice. Overall, this work highlights the potential of learning to be uncertain in difficult scenarios, compared to directly removing label noise.
%TODO: clear enough at this stage?
\end{abstract}

@@

% AMC, deep learning is being used. Different solutions
Communication systems often require the receiver to recognize the modulation scheme that has been used to encode the transmitted signals. The task is often referred to as Automatic Modulation Classification (AMC) and has applications ranging from detecting daily radio stations and managing spectrum resources, to eavesdropping and interfering with radio communications. The AMC task can be formulated as a Maximum likelihood (ML) estimation problem \cite{huan1995likelihood,dobre2007survey,hameed2009likelihood}, by computing the maximum of the likelihood function of the received signal with all possible modulations. Even if this solution is Bayes-optimal, sub-optimal approximations are used in practice \cite{dobre2007survey,Hameed_Dobre_Popescu_2009} because ML requires prior knowledge of the channel characteristics and is computationally complex to solve in realtime.

Deep learning \cite{goodfellow2016deep} has been proposed as a better solution for AMC as neural networks are relatively fast at inference time, adaptable to any channel characteristics, and their performance scales well with large quantities of data. Two classes of neural network architectures have been proposed for this task: long short-term memory networks (LSTMs) \cite{Rajendran_Meert_Giustiniano_Lenders_Pollin_2018,Guo_Jiang_Wu_Zhou_2020} and convolutional neural networks (CNNs) \cite{OShea_Corgan_Clancy_2016,West_OShea_2017,Sadeghi_Larsson_2019}. In particular, the authors in \cite{OShea_Roy_Clancy_2018} use a model based on the ResNet architecture \cite{Szegedy_Ioffe_Vanhoucke_Alemi_2016}, that outperforms all other CNN architectures. Other works use neural architecture search (NAS) \cite{ahmadi2008modulation,dai2019multi,perenda2021evolutionary} to trade off performance with computational speed. Even though neural networks currently represent the main and most effective method to tackle the AMC problem \cite{OShea_Roy_Clancy_2018}, they are very susceptible to adversarial perturbations, which compromises the security of the system against malicious attacks  \cite{Szegedy_Zaremba_Sutskever_Bruna_Erhan_Goodfellow_Fergus_2014, moosavi2017universal,Sadeghi_Larsson_2019,Lin_Zhao_2020,Flowers_Buehrer_Headley_2019, maroto2021benefits}. 
%\pf{that one can be shortened a bit if needed.}

@@

% Effect of adversarial perturbations.
Adversarial perturbations are carefully crafted but almost imperceptible disturbances that are added to the transmitted signal. These adversarial perturbations can be used as an effective way of jamming wireless communication systems as they require much less energy than normal attacks. Algorithms like FGSM \cite{Goodfellow_Shlens_Szegedy_2015} or PGD \cite{Madry_Makelov_Schmidt_Tsipras_Vladu_2019} can compute such perturbations by solving the following optimization problem:
\begin{equation}
\label{eq:adv_pert}
    \delta_i^* = \argmax_{\delta_i}\Ls(f_{\theta}(x_i + \delta_i), y_i) \quad \text{s.t.} \quad \lVert \delta_i \rVert_{\infty} \leq \varepsilon
\end{equation}
where $\delta_i^*$ is the adversarial perturbation added to the received signal $x_i$, $y_i$ is the one-hot-encoded vector of length K that encodes the modulation used, $\Ls$ is the cross-entropy loss, $f_{\theta}$ is the neural network defined with weights $\theta$, and $\varepsilon$ is a fixed value that constrains the norm of the perturbation to be small and imperceptible. On the other hand, adversarial training \cite{maroto2021safeamc,manoj2022toward}, randomized smoothing \cite{kim2021channel,manoj2022toward} and Generative Adversarial Networks (GANs) \cite{wang2022gan} have been shown to be effective in increasing the robustness of AMC models. But, in addition to being computationally costly, these defenses greatly reduce the accuracy of the model on clean data.
%\pf{be clear on limitations of the above}.

Some works from computer vision have tried to understand why networks are so susceptible to attacks, and label noise has been pointed to as one of the main causes \cite{sanyal2020benign}. Knowledge distillation~\cite{hinton2015distilling,romero2014fitnets,zagoruyko2016paying,chebotar2016distilling} can reduce this effect by training a student model to match the outputs of a teacher model. While knowledge distillation has been used in AMC~\cite{ma2020cross}, some computer vision works~\cite{goldblum2020adversarially,zi2021revisiting,shao2021and,maroto2022benefits} have shown that to achieve adversarial robustness, the outputs of the student model have to be matched on adversarial examples as well. And, to achieve a significant increase in robustness, both the teacher and the student models have to be trained adversarially, which can be very costly computationally.

% Our work, what are the main motivations. Contributions.
In this work, we build on the above observations and propose a new data-centric method to make neural networks more accurate and robust to adversarial attacks. We make the hypothesis that the information given by the original labels is limited, and does not encode the difference in uncertainty between low and high SNR signals. 
%TODO: contributions, models
Therefore, we propose to bring better information to the model by distilling the theoretical class probabilities derived from the offline maximum likelihood function estimation. 
%TODO: + add a couple of sentences about the selection/the proposed model + talk about adversarial training part
We show experimentally that such knowledge distillation permits to achieve better accuracy and adversarial robustness, compared with using the original labels or removing label noise. 
%TODO: explain results
Then, we show similar increases in performance when we combine this approach with adversarial training, where we train the model to match the distilled labels on adversarial examples. We highlight, that despite maximum likelihood being limited to offline settings, we see a clear benefit in the resulting model even in online settings. We claim that helping the model be uncertain in challenging scenarios is a promising direction with relevance outside of AMC settings, further validating the intuition that the choice and the quality of the training data are highly influential on the adversarial robustness of the model.
%\pf{talk about the robustness aspects, and adversarial training, how is it performed} \pf{talk about robustness results} \pf{recall benefits of the proposal, provide perspectives... how great is that? where do we go from there?}

@@

The communication system that characterizes the AMC task is shown in Figure \ref{fig:comm_system} with the gray blocks. It is composed of the transmitter, the communication channel, and the receptor. The transmitter is composed of a modulator and a communication filter $r'(x)$. The modulator uses a specific mapping to convert the data into a sequence of symbols. The symbols are upsampled and passed through the communication filter (e.g., root-raised cosine) to avoid inter-symbol interference (ISI). The signal is transmitted through the communication channel, which inevitably adds noise and distortion to the signal. The receptor is composed of another communication filter $r(x)$, that downsamples and transforms the signal back into symbols, and the demodulator, which converts the symbols into data.

Automatically choosing the correct demodulator based on the signal received is the problem that AMC tries to solve. 
In practice, we distinguish between two scenarios: the coherent scenario, where we have complete knowledge of the system and it is only valid in offline settings; and the non-coherent scenario, where some or all the channel and transmitter characteristics are unknown. The latter is generally used in online settings, as well as to test the model effectiveness in real conditions.

When training neural networks to perform well in AMC or any other task, one optimizes them to be as confident and accurate as possible on a given training set. In the case of AMC, that set is composed of the received signals and their corresponding labels describing the modulation used in the form of one hot encoded vectors. Our claim is that these labels are not good enough to train the model in the AMC task. The reason is that for noisier and heavily distorted signals, there is a non-negligible probability that the signal received was generated from a different modulation than the one we are enforcing the model to predict. Such cases are numerous when testing models in the AMC literature. Therefore, we want train our model with better information so that it can express this uncertainty with less confident predictions. Luckily, in AMC, there is an analytical model that can give us the probability vectors needed to train the model: the Maximum likelihood function.

@@

In many tasks, it can be difficult or even impossible to estimate the true probability of a sample belonging to a particular class. However, in AMC, we can use the Maximum likelihood (ML) function to derive these probabilities. Due to the characteristics of ML, this is only computationally feasible in coherent scenarios, where we have prior knowledge of the channel conditions. Particularly, if we assume that the channel is gaussian with variance $\sigma^{2}$, and that we know the proper communication filter $r(\cdot)$ that matches the filter $r'(\cdot)$ used in transmission, then the ML function is given by the following expression
\begin{equation}
	f_{i}(r(x)) = \dfrac{1}{2\pi \sigma^{2}|M_i|}\prod_{t=1}^{T} \sum_{j=1}^{|M_i|} \exp\left(-\dfrac{\lVert r(x)_t - s_j\rVert^{2}}{2 \sigma^{2}}\right)
\label{eq:ml}
\end{equation}
where $f_{i}$ is the ML function for a given modulation $M_i$ with $|M_i|$ number of states, $T$ is the number of symbols, $x$ is the received signal before the communication filter, $r(x)_t$ is the t-th symbol received, and $s_j$ is the symbol that corresponds to the state $j$. Given a set of modulations, the probability of a modulation $M_i$ would be $p_{ML}^{(i)}(x) = \log(f_{i}(r(x))) / \sum_i \log(f_{i}(r(x)))$. Note that the ML function directly processes $r(x)$ instead of $x$, as shown in Figure \ref{fig:comm_system}.

The reason why ML is not used in practice is simple: they perform badly in non-coherent scenarios, where the channel or transmission filter parameters are unknown. Moreover, any small deviation from the real channel parameters has a major effect on the ML performance, which discards the possibility of trying to estimate these parameters. Finally, incorporating the parameter uncertainty in the ML formulation makes it much more costly computationally, without being more performant than neural networks.

Based on these limitations, we propose a hybrid approach. We will use a neural network for inference, but we will train it with the probabilities computed offline with ML, to give the model this additional uncertainty information. Because Eq. \eqref{eq:ml} is limited to gaussian channels, we will remove the Rayleigh/Rician component of the channel when computing the ML probabilities. This is feasible when we consider that we can have full knowledge of the channel conditions by generating the training samples ourselves. Moreover, after training the neural network, ML is no longer needed, so that our model can be used in non-coherent scenarios, which correspond to real communication systems.

@@

In the AMC literature, neural networks are generally trained with the standard training (ST) loss
\begin{equation}
    \text{ST} : \dfrac{1}{N}\sum_{i}\Ls(f_{\theta}(x_i), y_i)
\end{equation}
where $N$ is the size of the training set.

However, our proposal is to provide the model with labels that better express the uncertainty of highly corrupted signals. Thus, using similar principles as knowledge distillation, we propose to match the neural network outputs with the output of ML in its corresponding coherent scenario.
\begin{equation}
    \text{ST\_ML} : \dfrac{1}{N}\sum_{i}\Ls(f_{\theta}(x_i), p_{ML}(r(x_i)))
\label{eq:st_ml}
\end{equation}
where $p_{ML}$ gives the class probabilities from applying the Maximum Likelihood function, and $r$ is the function that uses the coupled receiver filter and downsamples the signal. Because $r$ and $p_{ML}$ are functions that depend on information that is not known in non-coherent scenarios, we propose to use this loss function only when training the network, where this information can be known.

The main downside of using this function is that, while the probabilities given by ML are optimal in the context of a coherent scenario, they differ from the real probabilities $p^{*}$ that are conditional to the channel and communication filter distributions, $H$. However, our hypothesis, which we test in Section \ref{sec:experiments}, is that training with $p_{ML}$ is going to be a better match to the optimal probabilities $p^{*}$ than the labels $y$ themselves, which rather enforce full confidence on all samples, no matter how noisy they are. Mathematically, these probabilities are related by the following expression:
\begin{equation}
	p[m|x] =  \sum_i p[m|x,H=h_i] \cdot p[H=h_i|x]
\end{equation}
where $m$ is the vector of all modulations, $h_i$ is one possible choice of channel and transmitter parameters. Thus, $p[m|x] = p^{*}$ and $p_{ML} = p[m|x,H=h_0]$. Based on this formulation, our model will match better $p^{*}$ when the true communication parameters $H=h_0$ can be easily predicted from x ($p[H=h_0|x] \approx 1$) or when the communication parameters do not affect that much the probabilities ($p[m|x,H=h_i] \approx p_{ML}, \; \forall i$).

Additionally, we propose a middle-ground approach, where instead of training the model on the ML probabilities, we use these probabilities to determine if the true label is incorrect. This happens in very noisy scenarios, where the noise added to the signal may change the true class of the signal by pure chance. Intuitively, training on these signals will potentially confuse the network. Thus, we will use the standard training loss but training only on the signals without label noise:
\begin{equation}
    \text{ST\_LNR} : \dfrac{1}{|D|}\sum_{i \in D}\Ls(f_{\theta}(x_i), y_i)
\end{equation}
where a training signal $i$ is in the subset $D$ if and only if $\argmax(y_i) = \argmax(p_{ML}(r(x_i)))$.
%TODO: motivate/explain. Why you have two solutions, and clearly say if they are fully independent.

@@

Robust models offer more security against adversarial attacks, but they are also more interpretable, basing their decisions on sensible features for the AMC task, like the quadrature and in phase components of the symbols \cite{maroto2021safeamc}. One of the most straightforward ways to improve the network robustness is to use the adversarial training (AT) loss function
\begin{equation}
    \text{AT} : \dfrac{1}{N}\sum_{i}\Ls(f_{\theta}(x_i'), y_i)
\end{equation}
where $x_i' = x_i + \delta_i^*$ is a crafted adversarial signal that maximizes the cross-entropy loss of the neural network in the neighborhood of $x_i$. Because the adversarial perturbation is dependent on the model weights, it has to be computed at each training iteration, typically using PGD.

Analogously to Eq. \eqref{eq:st_ml}, we propose the following adversarial loss, in which the original labels are replaced with the ML probabilities:
\begin{equation}
    \text{AT\_ML} : \dfrac{1}{N}\sum_{i}\Ls(f_{\theta}(x_i'), p_{ML}(r(x_i')))
\end{equation}
We highlight that the ML function assumes that the signal is distorted with gaussian noise, which is not accurate since the input was adversarially perturbed. However, during adversarial training the adversarial perturbation typically is very small, so we can make the assumption that the combination of the channel gaussian noise and the adversarial noise is approximately gaussian with energy $\sigma_F^{2} = \sigma^{2} + \varepsilon^{2}$.

One way to reduce the effect of this assumption is to instead remove the label noise using ML
\begin{equation}
    \text{AT\_LNR} : \dfrac{1}{|D|}\sum_{i \in D}\Ls(f_{\theta}(x_i'), y_i)
\end{equation}
where a training signal $i$ is in the subset $D$ if and only if $\argmax(y_i) = \argmax(p_{ML}(r(x_i')))$. 
% TODO: clarify flow of ideas!
Even if $p_{ML}$ is not strictly correct due to the adversarial perturbation being relatively large, it will tend to remove signals that are already very noisy, thus greatly reducing the chance of label noise affecting adversarial training. Since label noise has a direct impact on the robustness of the network, we expect label noise removal to be particularly effective.
% TODO: the structure of ideas, and why you propose AT, then AT_ML, then AT_LNR, is not clear: motivate + explain what is the final proposal and why

% TODO: not clear!
For training with non-gaussian channels, because we remove the Rayleigh/Rician components for the ML function, we have the drawback that we cannot directly translate the adversarial perturbation added to the neural network to the signal received by ML. For that reason, we have considered the following two solutions: to use the ML probabilities of the uncorrupted signal
\begin{equation}
    \text{AT\_NML} : \dfrac{1}{N}\sum_{i}\Ls(f_{\theta}(x_i'), p_{ML}(r(g_i))
\label{eq:at_nml}
\end{equation}
and to use the adversarial example given by the ML function
\begin{equation}
    \text{AT\_AML} : \dfrac{1}{N}\sum_{i}\Ls(f_{\theta}(x_i'), p_{ML}(r(g_i)'))
	\label{eq:at_aml}
\end{equation}
where $g_i$ is the received signal after removing the Rayleigh/Rician components, and $r(g_i)'$ is a crafted adversarial signal that maximizes the cross-entropy loss of ML in the neighborhood of $r(g_i)$.
Because adversarial attacks can significantly change the probabilities of the received signal, we always recommend to use AT\_AML over AT\_NML.
%TODO: again, not very clear about what is the final propsal and why? in what settings?

@@

We propose to evaluate our proposal on scenarios with different levels of non-coherence in the wireless channel. This way, we can verify if the probabilities generated by ML in a coherent scenario are useful to train the model even if it is tested on varying channel and transmitter conditions.
